# Figures

```{r,echo=FALSE}
setwd("C:/Users/mcolvin/Documents/projects/MS-Pallids/analysis")
	source("./src/1_global.R")  	
	source("./src/2_functions.R")         
	source("./src/3_load.R")     
  	source("./src/4_clean.R" )
 	source("./src/5_tables.R") 
	source("./src/6_figures.R") 
	source("./src/7_model.R")
```



```{r, echo=FALSE,dpi=200,fig.cap=NULL}
figures(1)
```
Figure 1.  Lower Mississippi River tempeature and 
stage over the study period for Catfish Point river segement.



```{r, echo=FALSE,dpi=200,fig.cap=NULL}
figures(2)
```
Figure 2.  Lower Mississippi River tempeature and 
stage over the study period for Tara to Vicksburg 
river segement.



```{r, echo=FALSE,dpi=200,fig.cap=NULL}
figures(4)
```
Figure 3.  Predicted habitat availability at varying river 
stages for Catfish Point (top panel) and Tara to Vicksburg 
(bottom panel) segments of the lower Mississippi River.  

```{r, echo=FALSE,dpi=200,fig.cap=NULL}
figures(5)
```
Figure 3.  Predicted habitat availability at varying river 
Temperature at average stage.  Predicted values for the 
lower Mississippi River segment located at Catfish Point.
Top panel represents actual probabilities of use and bottom
panel represents cumlative probabilities.  

```{r, echo=FALSE,dpi=200,fig.cap=NULL}
figures(6)
```

Figure 4.  Predicted habitat availability at varying river 
stage at average temperature.  Predicted values for the 
lower Mississippi River segment located at Catfish Point.
Top panel represents actual probabilities of use and bottom
panel represents cumlative probabilities. .  


```{r, echo=FALSE,dpi=200,fig.cap=NULL}
figures(5)
```

Figure 5.  Predicted habitat availability at varying river 
Temperature at average stage.  Predicted values for the 
lower Mississippi River segment extending from Tara downstream to
Vicksburg.  Top panel represents actual probabilities of use and bottom
panel represents cumlative probabilities. 




```{r, echo=FALSE,dpi=200,fig.cap=NULL}
figures(7)
```
Figure 6. Predicted habitat availability at varying river 
Temperature at average stage.  Predicted values for the 
lower Mississippi River segment extending from Tara downstream to
Vicksburg.  Top panel represents actual probabilities of use and bottom
panel represents cumlative probabilities. 
