
# Figures

```{r,echo=FALSE,warning=FALSE,message=FALSE}
setwd("C:/Users/mcolvin/Documents/projects/PSM/analyses/Transport-Mortality/analysis/")
	source("./src/1_global.R")  	
	source("./src/2_functions.R")         
	source("./src/3_load.R")     
  	source("./src/4_clean.R")
 	source("./src/5_tables.R") 
	source("./src/6_figures.R") 
	source("./src/7_models.R")
```



```{r, echo=FALSE,dpi=300,fig.cap="",warning=FALSE}
 figures(1)
```

Figure 1.  Study area and location of tributary populations of interest.
Open squares denote the first impassible major tributary dams.
The open triangle denotes the location of Willamette Falls.
Arrow denotes north and direction of river flow.  



```{r, echo=FALSE,dpi=300,fig.cap="",warning=FALSE}
figures(2)
```

Figure 2.  Predictions (solid black line) and 95% prediction interval (gray area) for models
representing hypotheses predicting the mortality rate of transported Chinook Salmon.
Panels represent prediction for models retained in the confidence model set for Foster
(panel a) and Dexter Dam (panel b).  



```{r, echo=FALSE,dpi=300,fig.cap="",warning=FALSE}
figures(3)
```

Figure 3.  Optimal transportation policies for spring-run Chinook Salmon trapped at Foster Dam.
The white lines denote commonly used tank volumes (300, 1200, 1500, 2000, 2700 gallons) in Upper 
Willamette River spring-run Chinook Salmon translocation. 
 
NOTE: What is going on here is there is a benefit of more trips because it reduces the loading time,
The 'flickering' is in part due to ties and how density is handled.  So this is a policy of load up 
a few fish and go rather than waiting a long time even if fish are at low densities in the truck.
Loading times are very high for Foster, much higher than Dexter but loaded densities are much lower.
Figure 3 and Figure 4 are still preliminary as I am working out some of the flickering.
Although Figure 4 behaves as one would expect and I do not anticipate it changing much.
 

```{r, echo=FALSE,dpi=300,fig.cap="",warning=FALSE}
figures(4)
```

Figure 4.  Optimal transportation policies for spring-run Chinook Salmon trapped at Dexter Dam.
The white lines denote commonly used tank volumes (300, 1200, 1500, 2000, 2700 gallons) in Upper
Willamette River spring-run Chinook Salmon translocation.  