# Tables

```{r,echo=FALSE,warning=FALSE, message=FALSE}
setwd("C:/Users/mcolvin/Documents/projects/PSM/analyses/Transport-Mortality/analysis/")
	source("./src/1_global.R")  	
	source("./src/2_functions.R")         
	source("./src/3_load.R")     
  	source("./src/4_clean.R" )
 	source("./src/5_tables.R") 
	source("./src/6_figures.R") 
#	source("./src/7_models.R")
```


Table 1.  Candidate explanatory variables, descriptions, and hypotheses. 

```{r, echo=FALSE}
tbl1<- tables(1)
kable(tbl1,digits=2,caption = NULL,row.names=FALSE,align=c('l','l','l'),
	col.names=c("Predictor type","Predictor","Description and hypothesis"))
```

Table 2. Summary of candidate variable used to evaluate the factors related to Chinook Salmon transport mortality in the Upper Willamette Basin.

```{r, echo=FALSE}
tbl2<- tables(2)
kable(tbl2,digits=2,caption = NULL,row.names=FALSE)
```

Table 3. Candidate models and model selection criteria for the set of candidate models for 
adult spring Chinook Salmon transport mortality. All models contained an intercept and 
a random effect of sample in addition to the variable being evaluated.  Models retained for 
full model; cumulative model weight ≤ 0.95.

```{r, echo=FALSE}
tbl3<- tables(3)
kable(tbl3,digits=2,caption = NULL,row.names=FALSE)
```

 
  
  
  
  
Table 4. Parameter estimates and 95% confidence limits (CL) of fixed and random effects 
for best approximating model of adult Chinook Salmon transport mortality. 
Random effects are variance components. 

```{r, echo=FALSE,warining=FALSE,message=FALSE}
tbl4<- tables(4)
kable(tbl4,digits=2,caption = NULL,row.names=FALSE)
```

